---
title: "ggplot_hook_codechunk"
author: "Parth"
date: "2024-06-24"
output: github_document
---

## Setting up my environment
Notes : Setting up my environment by loading `tidyverse` and `palmerpenguins`
packages

```{r loading packages}
library(tidyverse)
library(palmerpenguins)
```

## Visualizations
Here we will go through a series of visualizations

### Flipper and body mass in purple
Here, we plot flipper length against body mass

```{r}
ggplot(data=penguins,aes(x=flipper_length_mm,y=body_mass_g))+
  geom_point(color="purple")
```

### Flipper and body mass by species
Here, we plot flipper length against body mass and look at the breakdown by 
species

```{r}
ggplot(data=penguins,aes(x=flipper_length_mm,y=body_mass_g))+
  geom_point(aes(shape=species))
```

### Flipper and body mass by species and sex
Here, we plot flipper length against body mass and look at the breakdown by
species and sex

```{r}
ggplot(data=penguins,aes(x=flipper_length_mm,y=body_mass_g))+
  geom_point(aes(color=species,
                 shape=species)) +
  facet_wrap(~sex)
```









